### 2021-04-17 README.rmd
testthat is added to suggested package (it was missing and not mentionned by rcmd check, weird)

Please note that the `Vizumap` project is released with a [Contributor Code of Conduct](CONDUCT.md). By contributing to this project, you agree to abide by its terms.

@@

`Vizumap` version 1.2.0 is licensed under [GPLv3](LICENSE.md).

## History of Vizumap

Vizumap began as a visualisation project at the University of Missouri in 2016. Chris Wikle, professor of statistics, posed an interesting research question to Lydia Lucchesi, a student curious about data visualisation and R.

How do you include uncertainty on a map displaying areal data estimates?

Over the course of a year, they put together three methods for visualising uncertainty in spatial statistics: the bivariate choropleth map, the pixel map, and the glyph map. By mid-2017, there were maps, and there was a lot of R code, but there was not a tool that others could use to easily make these types of maps, too. That’s when statistician Petra Kuhnert recommended developing an R package. Over the course of a month, Petra and Lydia developed Vizumap (originally named VizU) at CSIRO Data61 in Canberra, Australia. Since then, the package has been expanded to include exceedance probability maps, an uncertainty visualisation method developed by Petra while working on a Great Barrier Reef (GBR) project.

Vizumap has been used to visualise the uncertainty of American Community Survey estimates, the prediction errors of sediment estimates in a GBR catchment, and most recently the [uncertainty of estimated locust densities in Australia](https://www.nature.com/articles/s41598-020-73897-1/figures/4). We would like to assemble a Vizumap gallery that showcases different applications of the package’s mapping methods. If you use Vizumap to visualise uncertainty, please feel free to send the map our way. We would like to see it!

## References

Kuhnert, P.M., Pagendam, D.E., Bartley, R., Gladish, D.W., Lewis, S.E. and Bainbridge, Z.T. (2018) [Making management decisions in face of uncertainty: a case study using the Burdekin catchment in the Great Barrier Reef, Marine and Freshwater Research](https://publications.csiro.au/publications/#publication/PIcsiro:EP168206), 69, 1187-1200, https://doi.org/10.1071/MF17237.

Lucchesi, L.R. and Wikle C.K. (2017) [Visualizing uncertainty in areal data with bivariate choropleth maps, map pixelation and glyph rotation](http://faculty.missouri.edu/~wiklec/LucchesiWikle2017Stat), Stat, https://doi.org/10.1002/sta4.150.

>>>>

Please note that the `geocmeans` project is released with a [Contributor Code of Conduct](CONDUCT.md). By contributing to this project, you agree to abide by its terms.

@@

`geocmeans` version 0.1.0 is licensed under [GPL2 License](LICENSE.txt).
